SDG contributions

### 2023-09-15 article/article.qmd
WS, typo & figure tweaks

p1 +
    geom_smooth(aes(colour = NULL), alpha = .3, show.legend = FALSE,
                colour = "grey30") +
  labs(colour = "World region")
```
### split by SDG
```{r}
oa_per_country_per_SDG <- oa_per_affiliation_selected %>%
  filter(year >= 2015 & year <= 2018) %>% 
  group_by(country, SDG_label, is_oa) %>%
  summarise(sum_frac_oa = sum(frac_count)) %>%
  mutate(prop_oa = sum_frac_oa/sum(sum_frac_oa),
         sum_frac_total = sum(sum_frac_oa)) %>%
  collect()

@@

```{r oa_prestige_correlation, fig.width=8, fig.height=4}
affil_oa %>% 
  group_by(year, SDG_label) %>% 
  filter(n_frac_papers > 50) %>% 
  summarise(cor = cor(oa_share, P_top10, use = "pairwise.complete.obs")) %>% 
  ggplot(aes(year, cor, colour = fix_sdg(SDG_label))) +
  geom_line() +
  geom_point() +
  colorspace::scale_color_discrete_qualitative() +
  scale_y_continuous(limits = c(0, .6)) +
  labs(y = expression(paste("Correlation between OA shares in SDG & P"["top 10%"])),
       x = NULL, colour = NULL) +
  theme(legend.position = "top")
```

>>>>

p1 +
    geom_smooth(aes(colour = NULL), alpha = .3, show.legend = FALSE,
                colour = "grey30") +
  labs(colour = "World region")
```
### Split by SDG
```{r}
oa_per_country_per_SDG <- oa_per_affiliation_selected %>%
  filter(year >= 2015 & year <= 2018) %>% 
  group_by(country, SDG_label, is_oa) %>%
  summarise(sum_frac_oa = sum(frac_count)) %>%
  mutate(prop_oa = sum_frac_oa/sum(sum_frac_oa),
         sum_frac_total = sum(sum_frac_oa)) %>%
  collect()

@@

```{r oa_prestige_correlation, fig.width=6.5, fig.height=3.7}
affil_oa %>% 
  group_by(year, SDG_label) %>% 
  filter(n_frac_papers > 50, !is.na(P_top10)) %>% 
  summarise(cor = cor(oa_share, P_top10, use = "pairwise.complete.obs")) %>% 
  ggplot(aes(as_year(year), cor, colour = fix_sdg(SDG_label))) +
  geom_line() +
  geom_point() +
  colorspace::scale_color_discrete_qualitative() +
  scale_y_continuous(limits = c(0, .6)) +
  labs(y = expression(paste("Correlation between OA shares in SDG & P"["top 10%"])),
       x = NULL, colour = NULL) 
```
